\TheTitle

### 2016-04-26 linvis.tex
Updating Related Work section and adding citation
Condensing the related work section, still more to be done for it.
Adding citations for bubble tree.

\begin{figure}[htbp]
  \centering
        \includegraphics[width=\columnwidth]{figures/events.pdf}
  \caption{Example of a sequence of events performed in different repositories. The horizontal axis represents time. Each horizontal section represents a
    different branch and/or repository. Each commit points to its ancestor.}
  \label{fig:repoEvents}
\end{figure}

@@

The bubble tree (figure \ref{fig:bubble_tree}) provides a very clear picture of
where a commit is located in the tree hierarchy. The currently selected commit or merge
is colored red, while non-selected merges use a shade of blue and commits use white.
The depth of the blue colouring is dependent on how deep in the hierarchy that node
is. The root is the lightest blue, and the contained merges are progressively
darker.

@@

Many of the tools work to address the issues of communication between developers and
inter-team collaboration. Codebook uses a mining technique to determine the
developer of a piece of code, the program manager who wrote the specification for
the code, and the program managers and developers on the team who were working
together\cite{Begel2010}. This is designed to help collaboration between developers
on a project while the project is being developed.  In maintaining the code, the
code has already been written, the original developer many not have seen this piece
of code in years, and will most likely have moved to another problem. If the
maintainer is pulling from a part of the kernel that has been recently updated, in
the event of a zero-day attack for instance, the information about who is developing
that portion of the kernel is of use; however, if the maintainer is pulling from
sections that are older, then the maintainer must be able to understand the code
using the provided tools, not the original developer.

Hipikat is another tool with a focus on communication issues between developers. It
is designed for non-collocated teams, helping new developers understand design
decisions of the system \cite{Cubranic2005}. It records artifacts about the project
to build a "memory" of the project development that new users can work with to
understand where and how to make modifications in large projects. The artifacts are
recorded using tools like bugzilla and CVS. Such a tool could prove useful in
understanding the changes between a maintainer's current version of an older kernel
and the changes being made to the current master version of the kernel.

These tools work toward assisting the communications between developers and
providing a summary of the project. Our goal includes providing a visual summary of
the topology of the repository, as well as providing a summary of the changes made
at a location within the repository. EPOSee, Gource, and Gitk are all tools designed
for visualizing various aspects of repositories.

EPOSee is a tool for visualizing changes that often happen simultaneously in a
commit or as a sequence of events \cite{Burch2005}. It produces visualizations about
the confidence that changes are made either together or sequentially. For instance,
changes in the header file may also indicate that a change was made in the
implementation file. The visualization tool is designed to visualize implicit rules
about the order of operations on various files, if too many outliers are detected,
the project manager may want to restructure the project.  While this is useful for
new projects, the development model of the Linux kernel is already structured and is
unlikely to change without good reasons behind it.

@@

@@

\nocite{*}

>>>>

\evan{pdfs are not included in the repository}
\begin{figure}[htbp]
  \centering
        \includegraphics[width=\columnwidth]{figures/events.pdf}
  \caption{Example of a sequence of events performed in different repositories. The horizontal axis represents time. Each horizontal section represents a
    different branch and/or repository. Each commit points to its ancestor.}
  \label{fig:repoEvents}
\end{figure}

@@

Bubble trees are useful for providing a clear visualization of hierarchal
data\cite{Boardman2000}. The bubble tree (figure \ref{fig:bubble_tree}) provides a
very clear picture of where a commit is located in the tree hierarchy. The currently
selected commit or merge is colored red, while non-selected merges use a shade of
blue and commits use white.  The depth of the blue colouring is dependent on how
deep in the hierarchy that node is. The root is the lightest blue, and the contained
merges are progressively darker.

@@

Many tools work to address the issues in communication between developers in
inter-team collaboration work. Codebook \cite{Begel2010} uses a data mining
technique  to determine the developer of a piece of code, the program manager who
wrote the specification for the code, and the program managers and developers on the
team who were working together. Hipikat\cite{Cubranic2005} is another tool with a
focus on communication. Where codebook focuses on developers working on a project,
Hipikat is focused on enabling easier integration of new developers to a project by
providing them with easily-searchable artifacts of the changes made. Codebook is
useful for pairing a contributor with the original developer; however, the developer
may not have worked with the piece of code in years. A Hipikat program may provide
more information to the maintainer as it records the artifacts of why certain
design decisions were made when they were made using other tools like Bugzilla and
CVS. In both cases, our goal includes providing a summary of the topology of the
kernel repository through a visual tree.

Most visualizers provide a visual presentation of a certain aspect of a repository.
Fractal Figures \cite{Ambros2005} uses a unit square to represent a portion of a
project, then partitions the square based on the proportion of an author's
contributions to that portion of the project. EPOSee\cite{Burch2005} and Evolution
Radar\cite{Ambros2009} perform further analysis, determine which files are made
together, and what changes are made over a sequence of commits, though the goals
behind these projects is different.

Codebook, Hipikat, Fractal Figures, EPOSee, and Evolution Radar all work with data
from CVS repositories. Our goal is to provide information about git repositories,
specifically the Linux master repository. Fewer tools are available for generating
visualizations and summaries of git repositories, potentially due to the DAG model
used by git.

@@

Our tool is primarily aimed at presenting the hierarchical structure of the Linux
git repository. We use tables for presenting the summarized information of the
commits and merges, but this information could also be presented in a graphical
form. Various graphical forms for displaying file and authorship data exist, the
principal forms being matrix views, city scapes, bar and pie charts, and networks
\cite{Eick2002}. Any of these data visualization metaphors are applicable to our
system.

@@

% \nocite{*}
